Are parental care induced gene expression patterns affect more by internal cues or external stimuli?

### 2019-09-07 docs/manipulation_manuscript.Rmd
remove cache

```{r, message=FALSE, warning=FALSE, cache=TRUE, echo = F, fig.width= 5}
library(cowplot)
ggdraw() + draw_image("../figures/manipulation/offspringremoval-1.png") 
```

>>>>

```{r, message=FALSE, warning=FALSE, cache=FALSE, echo = F, fig.width= 5, fig.cap= "Circulating prolactin levels with an without manipulation."}
ggdraw() + draw_image("../figures/hormones/prolactin-manip-1.png") 
```

```{r, message=FALSE, warning=FALSE, cache=FALSE, echo = F, fig.width= 5, fig.cap= "Offspring removal."}
ggdraw() + draw_image("../figures/manipulation/offspringremoval-1.png") 
```

```{r, message=FALSE, warning=FALSE, cache=FALSE, echo = F, fig.width= 5, fig.cap = "Manipulation of timing of hatch with dummy eggs and foster chicks. "}
ggdraw() + draw_image("../figures/manipulation/prolongextend-1.png") 
```
